---
title: "AS3-1: 數位偵探"
author: "第 14 組"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=F}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr, d3heatmap)
```
<hr>

犯罪是一個國際關注的問題，但它在不同的國家以不同的方式記錄和處理。 在美國，聯邦調查局（FBI）記錄了暴力犯罪和財產犯罪。 此外，每個城市都記錄了犯罪行為，一些城市發布了有關犯罪率的數據。 伊利諾伊州芝加哥市從2001年開始在線發布犯罪數據。

芝加哥是美國人口第三多的城市，人口超過270萬。在這個作業裡面，我們將關注一種特定類型的財產犯罪，稱為「汽車盜竊」，我們將使用R中的一些基本數據分析來了解芝加哥的汽車盜竊紀錄。請載入文件"data/mvtWeek1.csv"：以下是各欄位的描述：

+ `ID`: a unique identifier for each observation
+ `Date`: the date the crime occurred
+ `LocationDescription`: the location where the crime occurred
+ `Arrest`: whether or not an arrest was made for the crime (TRUE if an arrest was made, and FALSE if an arrest was not made)
+ `Domestic`: whether or not the crime was a domestic crime, meaning that it was committed against a family member (TRUE if it was domestic, and FALSE if it was not domestic)
+ `Beat`: the area, or "beat" in which the crime occurred. This is the smallest regional division defined by the Chicago police department.
+ `District`: the police district in which the crime occured. Each district is composed of many beats, and are defined by the Chicago Police Department.
+ `CommunityArea`: the community area in which the crime occurred. Since the 1920s, Chicago has been divided into what are called "community areas", of which there are now 77. The community areas were devised in an attempt to create socially homogeneous regions.
+ `Year`: the year in which the crime occurred.
+ `Latitude`: the latitude of the location at which the crime occurred.
+ `Longitude`: the longitude of the location at which the crime occurred.

<br>

- - -

###  Section-1 Loading the Data

【1.1】How many rows of data (observations) are in this dataset?
```{r}
#讀取資料
D=read.csv("data/mvtWeek1.csv")
#資料行數
nrow(D)
```

類別(Factor) versus 字串(Character)

【1.2】How many variables are in this dataset?
```{r}
#資料列數
ncol(D)
```


【1.3】Using the "max" function, what is the maximum value of the variable "ID"?
```{r}
#ID的最大值
max(D$ID)
```


【1.4】 What is the minimum value of the variable "Beat"?
```{r}
#Beat的最小值
min(D$Beat)
```


【1.5】 How many observations have value TRUE in the Arrest variable (this is the number of crimes for which an arrest was made)?
```{r}
#行竊遭逮捕的總次數
sum(D$Arrest=="TRUE") 
```

【1.6】 How many observations have a LocationDescription value of ALLEY?
```{r}
#行竊地點為巷弄的總次數
sum(D$LocationDescription=="ALLEY")
```


<br><br>

- - -

### Section-2 Understanding Dates in R

【2.1】 In what format are the entries in the variable Date?

+ Month/Day/Year Hour:Minute
+ Day/Month/Year Hour:Minute
+ Hour:Minute Month/Day/Year
+ Hour:Minute Day/Month/Year

```{r}
#將字串轉成時間
ts = as.POSIXct(D$Date, format="%m/%d/%y %H:%M")
#製作直方圖、呈現標題、將x軸的值由橫轉直、xy軸名稱
hist(ts,"year",main="histogram of ts",las=2,xlab="year", ylab="frequency")
```

```{r}
#列出一星期中每天遭到偷竊的次數
table(format(ts,"%u"))
#列出各個月份遭到偷竊的次數
table(format(ts,"%m"))
```

```{r}
#將一星期中每天遭到偷竊的次數＆各個月份遭到偷竊的次數 做出列聯表
table(month=format(ts,"%m"),weekday=format(ts,"%u"))
```

```{r fig.height=2.5, fig.width=8}
table(format(ts,"%u"), format(ts,"%H")) %>% 
  as.data.frame.matrix %>% 
  d3heatmap(F,F,col=colorRamp(c('lightgreen','orange','red')))
#製出熱圖
```


【2.2】 What is the month and year of the median date in our dataset? 
```{r}
#dataset的中位數
median(ts)
```

【2.3】 In which month did the fewest motor vehicle thefts occur?
```{r}
#將每月遭竊次數由小至大排列
sort(table(format(ts,"%m")))
```

【2.4】 On which weekday did the most motor vehicle thefts occur?
```{r}
#將一星期中每日遭竊次數由小至大排列
format(ts,"%u") %>% table() %>% sort()
```

【2.5】 Which month has the largest number of motor vehicle thefts for which an arrest was made?
```{r}
#將每月行竊遭逮捕的次數由小至大排列
ts[D$Arrest] %>% format("%m") %>% table %>% sort
```

<br><br>

- - -

### Section-3 Visualizing Crime Trends

【3.1】 (a) In general, does it look like crime increases or decreases from 2002 - 2012? (b) In general, does it look like crime increases or decreases from 2005 - 2008? (c) In general, does it look like crime increases or decreases from 2009 - 2011?
```{r}
par(cex=0.7)
#製作直方圖、呈現標題、將x軸的值由橫轉直、xy軸名稱
hist(ts,"year",main="histogram of ts",las=2,xlab="year", ylab="frequency")
```
Ans:
(a)decrease
(b)decrease
(c)increase

【3.2】 Does it look like there were more crimes for which arrests were made in the first half of the time period or the second half of the time period?
```{r}
#犯罪在2007以前(false)以及之後(true)的次數
table(ts>as.POSIXct("2007-01-01"))
```

【3.3】 For what proportion of motor vehicle thefts in 2001 was an arrest made?
```{r}
#將是否有被逮捕的資料與年份製出列聯表，以一欄作為100%，取到小數點第三位
table(D$Arrest, format(ts,"%Y")) %>% prop.table(2) %>% round(3)
```

【3.4】 For what proportion of motor vehicle thefts in 2007 was an arrest made?
```{r}
#依照年份找出被逮補的機率
tapply(D$Arrest, format(ts, 'Y'), mean) %>% round(3)
```

【3.5】 For what proportion of motor vehicle thefts in 2012 was an arrest made?
```{r}
#依照年份找出被逮補的機率
tapply(D$Arrest, format(ts, 'Y'), mean) %>% round(3)
```

<br><br>

- - -

### Section-4 Popular Locations

【4.1】 Which locations are the top five locations for motor vehicle thefts, excluding the "Other" category? You should select 5 of the following options.

```{r}
#列出被偷竊地點後進行排序
#因為sort結果是由小排到大，因此求前五高要取tail
#前五高包含"Other"，故tail要取6個
table(D$LocationDescription) %>% sort %>% tail(6)
```

【4.2】 How many observations are in Top5?
```{r}
#找出每個地點發生偷竊的次數並將其排序·列出前6大常發偷竊的地點後刪掉第4個(other)資料·最後將這些地點的名字設為top5這個變數
(top5=names(table(D$LocationDescription) %>% sort %>% tail(6))[-4]) 
  sum(D$LocationDescription %in% top5)
```

【4.3】 One of the locations has a much higher arrest rate than the other locations. Which is it? 
```{r}
#令包含在top5中的行竊地點為TOP5
TOP5=subset(D,LocationDescription %in% top5)
#對TOP5的行竊地點做逮捕率的排序
tapply(TOP5$Arrest, TOP5$LocationDescription, mean) %>% sort
```

【4.4】 On which day of the week do the most motor vehicle thefts at gas stations happen?
```{r}
#找出行竊地點在加油站的次數，將行竊地點發生在加油站的次數對其製表做排序
ts[D$LocationDescription=="GAS STATION"] %>% format("%a") %>% table %>% sort
```

【4.5】 On which day of the week do the fewest motor vehicle thefts in residential driveways happen?
```{r}
#找出行竊地點發生在住宅區汽車道的次數，將行竊地點的次數對其製表做排序
ts[D$LocationDescription=="DRIVEWAY - RESIDENTIAL"] %>% format("%a") %>% table %>% sort
```


<br><br><br>


