---
title: "AS3-3: 美國的人口統計和就業資料"
author: "第 14 組"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

就業統計數據是政策制定者用來衡量經濟整體實力的最重要指標之一。在美國，政府使用現有人口調查（CPS）衡量失業率，該調查每月收集來自各種美國人的人口統計和就業信息。在本練習中，我們將使用講座中審查的主題以及一些使用2013年9月版的，具有全國代表性的數據集。數據集中的觀察結果代表2013年9月CPS中實際完成調查的人員，完整數據集有385個欄位，但在本練習中，我們將使用數據集CPSData.csv版本，它具有以下欄位：

+ `PeopleInHousehold`: 受訪者家庭中的人數。
+ `Region`: 受訪者居住的人口普查區域。
+ `State`: 受訪者居住的州。
+ `MetroAreaCode`: 都會區代碼，如受訪者不住都會區，則為NA；從代碼到都會區名稱的對應在`MetroAreaCodes.csv`中提供。
+ `Age`: 受訪者的年齡，以年為單位。 80代表80-84歲的人，85代表85歲及以上的人。
+ `Married`: 受訪者的婚姻狀況。
+ `Sex`: 受訪者的性別。
+ `Education`: 受訪者獲得的最高教育程度。
+ `Race`: 受訪者的種族。
+ `Hispanic`: 受訪者是否屬於西班牙裔。
+ `CountryOfBirthcode`: 識別受訪者出生國家的代碼。從代碼到國家名稱的映射在CountryCodes.csv文件中提供。
+ `Citizenship`: 受訪者的公民身份。
+ `EmploymentStatus`: 受訪者的就業狀況。
+ `Industry`: 受訪者的就業行業（僅在受僱的情況下可用）。

- - -

<br><br>

###  Section-1 Loading and Summarizing the Dataset

__§ 1.1__ How many interviewees are in the dataset? answer: 131302
```{r}
#
#載入CPSdata資料
CPSData <- read.csv('data/CPSData.csv')
#透過str function 得知大略的資料狀態並得知共有131302個interviewees
str(CPSData)

#
```

__§ 1.2__ Among the interviewees with a value reported for the Industry variable, what is the most common industry of employment? Please enter the name exactly how you see it. answer:Educational and health services
```{r}
#
#透過table可以看到Industry產生次數分配表得知各個Industry的總數，再透過sort清楚看出哪個最多人
sort(table(CPSData$Industry),decreasing = TRUE)
#
```

__§ 1.3__ Which state has the fewest interviewees? answer:New Mexico
```{r}
#
#透過table可以看到Industry產生次數分配表得知各個State的總數，再透過sort清楚看出哪個最少人
sort(table(CPSData$State))
#
```

Which state has the largest number of interviewees? answer: California
```{r}
#
#透過table可以看到Industry產生次數分配表得知各個State的總數，再透過sort清楚看出哪個最多人
sort(table(CPSData$State),decreasing = TRUE)
#
```

__§ 1.4__ What proportion of interviewees are citizens of the United States? answer: 0.9421943
```{r}
#
#step 1:透過table得知有7590為Non-Citizen
table(CPSData$Citizenship)
#step 2:透過nrow知道總數為131302
nrow(CPSData)
#step 3:再以100%減去Non-Citizen，則為citizens of the United States的比例
1-7590/131302
#
```

__§ 1.5__ For which races are there at least 250 interviewees in the CPS dataset of Hispanic ethnicity? (Select all that apply.)  
answer: American Indian, Black, Multiracial and White
+ American Indian
+ Asian
+ cBlack
+ Multiracial
+ Pacific Islander
+ White

```{r}
#New York-Northern
#透過table可以看到Race以及Hispanic的交叉表得知各個Race中為Hispanic的總數看出哪個大於250
table(CPSData$Race, CPSData$Hispanic)
#
```

<br><br> 

- - -

###  Section-2 Evaluating Missing Values

__§ 2.1__ Which variables have at least one interviewee with a missing (NA) value? (Select all that apply.)

+ PeopleInHousehold
+ Region
+ State
+ MetroAreaCode
+ Age
+ Married
+ Sex
+ Education
+ Race
+ Hispanic
+ CountryOfBirthCode
+ Citizenship
+ EmploymentStatus
+ Industry

```{r}
#
#透過apply逐列，再透過is.na function 得知missing (NA) value 最後以any判斷出各列是否有出現na值
sort(apply(is.na(CPSData), 2, any))
#
```

__§ 2.2__  Which is the most accurate:
answer : The Married variable being missing is related to the Age value for the interviewee.this statemet is the most accurate.

+ The Married variable being missing is related to the Region value for the interviewee.
+ The Married variable being missing is related to the Sex value for the interviewee.
+ The Married variable being missing is related to the Age value for the interviewee. 
+ The Married variable being missing is related to the Citizenship value for the interviewee.
+ The Married variable being missing is not related to the Region, Sex, Age, or Citizenship value for the interviewee.

```{r}
#
#透過table得知Region, Sex, Age, Citizenship以及Married的na值對照得知Age最有相關
table(CPSData$Region, is.na(CPSData$Married))
table(CPSData$Sex, is.na(CPSData$Married))
table(CPSData$Age, is.na(CPSData$Married))
table(CPSData$Citizenship, is.na(CPSData$Married))
#
```


__§ 2.3__ How many states had all interviewees living in a non-metropolitan area (aka they have a missing MetroAreaCode value)? For this question, treat the District of Columbia as a state (even though it is not technically a state). answer: 2
```{r}
#
#透過is.na得知是否為 non-metropolitan area的interviewee，再#透過table可以看到State以及non-metropolitan的交叉表得知各個State中為non-metropolitan的總數，flase為0只有2個states
table(CPSData$State,is.na(CPSData$MetroAreaCode))
#
```

How many states had all interviewees living in a metropolitan area? Again, treat the District of Columbia as a state. answer: 3
```{r}
#
#step 1: 透過is.na得知是否為 non-metropolitan area的interviewee
#step 2: 再透過table可以看到State以及non-metropolitan的交叉表得知各個State中為non-metropolitan的總數，true為1只有3個states
table(CPSData$State,is.na(CPSData$MetroAreaCode))
#
```

__§ 2.4__ Which region of the United States has the largest proportion of interviewees living in a non-metropolitan area? answer: Midwest
```{r}
#
#step 1: 透過is.na得知是否為 non-metropolitan area的interviewee
#step 2: 再透過tapply看出各個Region的 non-metropolitan area的interviewee的平均(mean)
#step 3: 透過sort讓資料按照順序排序看出Midwest為最大比率
sort(tapply(is.na(CPSData$MetroAreaCode),CPSData$Region, mean),decreasing = TRUE)
#
```

__§ 2.5__ Which state has a proportion of interviewees living in a non-metropolitan area closest to 30%? answer:Wisconsin
```{r}
#
#step 1: 透過is.na得知是否為 non-metropolitan area的interviewee
#step 2: 再透過tapply看出各個State的 non-metropolitan area的interviewee的平均(mean)
#step 3: 透過sort讓資料按照順序排序看出Wisconsin為最接近30%的State
sort(tapply(is.na(CPSData$MetroAreaCode),CPSData$State, mean))
#
```

Which state has the largest proportion of non-metropolitan interviewees, ignoring states where all interviewees were non-metropolitan? answer:Montana
```{r}
#
#step 1: 透過is.na得知是否為 non-metropolitan area的interviewee
#step 2: 再透過tapply看出各個State的 non-metropolitan area的interviewee的平均(mean)
#step 3: 透過sort讓資料按照順序排序看出除了Alaska,Wyoming皆為non-metropolitan,最大的為Montana 
sort(tapply(is.na(CPSData$MetroAreaCode),CPSData$State, mean))
#
```

<br><br> 

- - -

###  Section-3 Integrating Metropolitan Area Data

__§ 3.1__ How many observations (codes for metropolitan areas) are there in MetroAreaMap? answer:271
```{r}
#
#載入MetroAreaCodes資料
MetroAreaMap <- read.csv('data/MetroAreaCodes.csv')
#透過str function 得知大略的資料狀態並得知共有271個observations
str(MetroAreaMap)
MetroAreaMap
#
```

How many observations (codes for countries) are there in CountryMap? answer:149
```{r}
#
#載入CountryCodes資料
CountryMap <- read.csv('data/CountryCodes.csv')
#透過str function 得知大略的資料狀態並得知共有149個observations
str(CountryMap)
CountryMap
#
```

__§ 3.2__ What is the name of the variable that was added to the data frame by the merge() operation?answer:MetroArea
```{r}
#
#step 1:透過merge將CPSData與MetroAreaMap合併,再透過MetroAreaCode與Code欄位比對,並且保留全部x(MetroAreaCode)
#step 2:透過str比對出CPSData有14個variables及CPS_area有15個variables得知增加一個variable,經對照後看出為MetroArea
CPS_area = merge(CPSData, MetroAreaMap, by.x="MetroAreaCode", by.y="Code", all.x=TRUE)
str(CPSData)
str(CPS_area)
#
```

How many interviewees have a missing value for the new metropolitan area variable? answer:34238
```{r}
#
#透過summary可以看到MetroArea有34238 missing values
summary(CPS_area)
#
```

__§ 3.3__ Which of the following metropolitan areas has the largest number of interviewees?answer:New York-Northern New Jersey-Long Island, NY-NJ-PA
```{r}
#
#透過table可以看到MetroArea產生次數分配表得知各個IMetroArea的interviewees總數，再透過sort清楚看出哪個最多人
sort(table(CPS_area$MetroArea),decreasing = TRUE)
#
```

__§ 3.4__ Which metropolitan area has the highest proportion of interviewees of Hispanic ethnicity? answer:Laredo, TX
```{r}
#
#step 1: 再透過tapply看出各個MetroArea的 Hispanic的interviewee的平均(mean)
#step 2: 透過sort讓資料按照順序排序看出Laredo, TX為最大比率
sort(tapply(CPS_area$Hispanic,CPS_area$MetroArea,mean),decreasing = TRUE)
#
```

__§ 3.5__ Determine the number of metropolitan areas in the United States from which at least 20% of interviewees are Asian.answer4
```{r}
#
#step 1: 再透過tapply看出各個MetroArea的 Asian的interviewee的平均(mean)
#step 2: 透過table次數分配表找出大於0.2的metropolitan areas共有四個
table(tapply(CPS_area$Race == "Asian",CPS_area$MetroArea,mean)>0.2)
#
```

__§ 3.6__  Passing na.rm=TRUE to the tapply function, determine which metropolitan area has the smallest proportion of interviewees who have received no high school diploma. answer: Iowa City, IA
```{r}
#
#step 1: 再透過tapply看出各個MetroArea的 Education中 No high school diploma的比率,並且移除NA值
#step 2: 再透過sort排序找出最小比率的metropolitan area為Iowa City, IA
sort(tapply(CPS_area$Education == "No high school diploma", CPS_area$MetroArea, mean,na.rm=TRUE))
#
```


<br><br> 

- - -

###  Section-4 Integrating Country of Birth Data

__§ 4.1__ What is the name of the variable added to the CPS data frame by this merge operation? answer:Country
```{r}
#
#step 1:透過merge將CPSData與CountryMap合併,再透過CountryOfBirthCode與Code欄位比對,並且保留全部x(CountryOfBirthCode)
#step 2:透過str比對出CPSData有14個variables及CPS_country有15個variables得知增加一個variable,經對照後看出為Country
CPS_country = merge(CPSData, CountryMap, by.x="CountryOfBirthCode", by.y="Code", all.x=TRUE)
str(CPSData)
str(CPS_country)
#
```

How many interviewees have a missing value for the new metropolitan area variable? answer:176
```{r}
#
#透過is.na得知Country的值是否為na
#再透過table得知是na值的總數
table(is.na(CPS_country$Country))
#
```

__§ 4.2__ Among all interviewees born outside of North America, which country was the most common place of birth? answer:Philippines
```{r}
#
#透過table得知country的次數分配 再透過sort看出其最常見的出生地為Philippines
sort(table(CPS_country$Country),decreasing = TRUE)
#
```

__§ 4.3__ What proportion of the interviewees from the "New York-Northern New Jersey-Long Island, NY-NJ-PA" metropolitan area have a country of birth that is not the United States? answer:0.309
```{r}
#
#step 1:將所有的資料合併透過CPS_cuntry 加上MetroAreaMap
#step 2:再透過table計算Country不為United States以及MetroArea為New York-Northern New Jersey-Long Island, NY-NJ-PA
#step 3:透過table看出共有1668人為題目所需再除以1668+3736
CPS_all = merge(CPS_country, MetroAreaMap, by.x="MetroAreaCode", by.y="Code", all.x=TRUE)
table(CPS_all$Country!='United States',CPS_all$MetroArea=='New York-Northern New Jersey-Long Island, NY-NJ-PA')
1668 / (3736+1668)
#
```

__§ 4.4__ Which metropolitan area has the largest number (note -- not proportion) of interviewees with a country of birth in India?  answer:New York-Northern New Jersey-Long Island, NY-NJ-PA
```{r}
#
#step 1: 再透過tapply看出各個MetroArea的 India的總和,並且移除NA值
#step 2: 再透過sort排序找出最大的metropolitan area為New York-Northern New Jersey-Long Island, NY-NJ-PA
sort(tapply(CPS_all$Country == "India", CPS_all$MetroArea, sum, na.rm=TRUE))
#
```

In Brazil? answer: Boston-Cambridge-Quincy, MA-NH
```{r}
#
#step 1: 再透過tapply看出各個MetroArea的 India的總和,並且移除NA值
#step 2: 再透過sort排序找出最大的metropolitan area為Boston-Cambridge-Quincy, MA-NH
sort(tapply(CPS_all$Country == "Brazil", CPS_all$MetroArea, sum, na.rm=TRUE))
#
```

In Somalia? answer: Minneapolis-St Paul-Bloomington, MN-WI
```{r}
#
#step 1: 再透過tapply看出各個MetroArea的 India的總和,並且移除NA值
#step 2: 再透過sort排序找出最大的metropolitan area為Minneapolis-St Paul-Bloomington, MN-WI
sort(tapply(CPS_all$Country == "Somalia", CPS_all$MetroArea, sum, na.rm=TRUE))
#
```

<br><br><br>
